I can see clearly now: reinterpreting statistical significance

### 2018-10-09 doc.tex
BMB comments/tweaks

In most biological studies, the null hypothesis is known or believed to not be strictly true.
Even in cases where the null hypothesis is sensible \citep[e.g., particle physics][]{Staley2017} \pval testing does not provide a route to confirmation.
This being the case, it is worth asking how NHST has survived ``if it is as idiotic as \ldots long believed''. 
\jd{Why does Morgan cite Kramer?} \citet{Kramer2011}.

The value of NHST can be seen in something like a permutation-based t-test \cite[Chapter 1]{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger. 
More generally, testing the null hypothesis is a proxy for asking whether we clearly see a signal of how our data differs from it.
In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. 
In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether something has been seen clearly.

>>>>

In most biological studies, the null hypothesis is known or believed to not be strictly true.
Even in cases where the null hypothesis is sensible \citep[e.g., particle physics][]{Staley2017} \pval testing does not provide a route to confirmation.
\bmb{¿ clarify ?}
This being the case, it is worth asking how NHST has survived ``if it is as idiotic as \ldots long believed''. 
\jd{Why does Morgan cite Kramer?}
\bmb{perhaps [IIRC] because it was an indirect ref?}
\citet{Kramer2011}.

The value of NHST can be seen in something like a permutation-based t-test \cite[Chapter 1]{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger. 
More generally, testing the null hypothesis is a proxy for asking whether we clearly see a signal of how our data differs from it.
In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. 
In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
